%%%% Document options
\documentclass[a4paper, 11pt]{article}
\usepackage[a4paper]{geometry}
%\usepackage[utf8x]{inputenc}
\usepackage{epsfig,rotating}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{multirow}
\usepackage{eurosym}
\usepackage{tabularx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage[version=3]{mhchem}
\usepackage{booktabs}

\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

%\usepackage[parfill]{parskip}    

\begin{document}
\input{Commands.tex}

% =============================
\title{\Huge{\sf Report to the NSCS committee}\\ \vspace{.5cm}
\LARGE{The NEXT collaboration} 
\vspace{.5cm}}


\date{ } % Activate to display a given date or no date
\maketitle
\thispagestyle{empty}
\clearpage

\setcounter{page}{1}
%\tableofcontents

% =============================
\section{Introduction}
\input{src/Introduction}

This document is organised as follows. 
In section \ref{sec.next} we summarise the principle of operation and status of the NEXT experiment. In section \ref{sec.bm} we present the NEXT background model and the expected sensitivity to the effective Majorana mass, \mbb.  In section \ref{sec.new}, we explain the R\&D program of the NEW apparatus, currently being commissioned at the Canfranc Underground Laboratory (LSC) in Spain. In section \ref{sec.ts}, we comment the prospects of the technology for the ton scale. In section \ref{sec.nc} we discuss the structure of the NEXT collaboration and the proposed sharing of responsibilities and costs with the USA contingent.  Finally, in section \ref{sec.conclu} we conclude.

\section{The NEXT experiment}
\label{sec.next}
\input{src/NEXT}

\section{NEXT background model and expected sensitivity to \mbb} 
\label{sec.bm}

\input{src/SignalAndBackground}
\input{src/SelectionCuts}
\input{src/BackgroundRate}
\input{src/SensitivityNext100}

\section{\label{sec.new}The NEW detector}
\input{src/NEW}

\section{Towards a ton-scale high-pressure xenon TPC.}
\label{sec.ts}
\input{src/TonScale}

\section{The NEXT collaboration}
\label{sec.nc}
 \input{src/NextCollaboration}

 \section{Conclusions}
 \label{sec.conclu}
 In this report we have presented a comprehensive status of the NEXT experiment and its  scientific goals (including R\&D) for the period 2015-2018. Demonstration with the NEW and NEXT-100 detector of the expected performance in energy resolution and background rejection would qualify the technology for a ton-scale detector capable of exploring the IH in a reasonable time (5 year) with a reasonable target mass (2 tons). Furthermore, the collaboration will be pursuing active R\&D to find suitable gas mixtures capable to reduce the diffusion to some 2 mm over 1 m drift length, without jeopardising other capabilities of the detector such as electron lifetime or energy resolution. Promising candidates (Xe + 0.1\% \COT, Xe + 0.5\% \CHF) are currently being investigated. The reduction of diffusion would increase the background rejection of the technique and would open the possibility of further improvement of the topological signature adding a magnetic field. A preliminary estimate of the cost estimate of a ton-scale apparatus yields a figure of 24 M\$ (assuming 15 M\$ for the cost of 1 ton of \XE\ which is a conservative estimate with respect to the cost payed by NEXT). The cost could be increased by perhaps 1 M\$ if a magnet would also be deployed.  
 
 \nocite{*}
\bibliographystyle{elsarticle-num}
\bibliography{biblio}
\end{document}
